Supplementary Information 1

### 2025-04-15 MS2_Krill.Rmd
add table summary

# ABSTRACT

@@

# INTRODUCTION

@@

# METHODOLOGY

@@

# RESULTS

@@

The residuals are visualized by year and length bin, allowing an assessment of model fit over time and across the size structure of the population (Figure \@ref(fig:pearson)). In the "Without Ecosystem Variables" scenario (top left), substantial lack of fit is evident across multiple years and length classes, particularly in the late 1990s and early 2000s. Positive Pearson residuals indicate that the model tends to underestimate frequencies of certain length bins, especially among smaller and mid-sized individuals, suggesting poor representation of recruitment and growth dynamics in the absence of environmental and predator effects. The "With Predator" scenario (top right) shows some improvement in model fit, with slightly more balanced residuals. However, there are still consistent deviations in the mid-size ranges across multiple years, indicating that predation alone does not fully explain observed variability in length composition. In the "With Environment" scenario (bottom left), there is a noticeable reduction in residual magnitude across several years and size classes, implying that incorporating environmental covariates helps align the model more closely with observed size distributions. This is particularly apparent in the early 2000s, where the residuals are closer to zero across most bins. Finally, the "With Predator and Ecosystem" scenario (bottom right) shows the most consistent reduction in Pearson residuals across time and size structure. The distribution of residuals is more homogeneous and centered around zero, indicating that the combined inclusion of predator and environmental drivers leads to the best model fit among the four scenarios.

```{r pearson, eval=TRUE, fig.cap= "Pearson residuals of predicted versus observed length-frequency distributions of Antarctic krill across four modeling scenarios (s1.1 to s1.4), each incorporating increasing levels of ecosystem complexity. Residuals are shown by fleet, survey, and predator source, allowing visual assessment of model fit across time and sampling components"}
knitr::include_graphics('Figs/Pearson.png')
```

@@

The comparative evaluation of the four model scenarios (s1.1–s1.4) revealed key differences in model performance and complexity (Table \@ref(tab:diagnostics)). Scenario s1.1, the simplest model with no ecosystem covariates, exhibited the lowest maximum gradient component (2.4e−05), suggesting a well-converged solution. It also used the fewest estimated parameters (94) and achieved a relatively low RMSE (0.88), indicating a good fit to the data despite its simplicity. However, its negative log-likelihood (NLL = 1,291.04) was higher compared to more complex models. Model s1.2, which includes only environmental covariates, showed a substantial increase in the likelihood fit (NLL = 25,963.90), although it also required a larger number of parameters (152). Similarly, s1.3, which includes only predator effects, maintained a moderate parameter count (140) but performed slightly worse in terms of RMSE (0.93), indicating potential overfitting or reduced explanatory power relative to model complexity. The full model, s1.4, incorporating both environmental and predator effects, achieved a strong likelihood value (NLL = 25,188.80), albeit with the highest number of parameters (175). Its RMSE (0.89) was similar to the other scenarios, suggesting that the inclusion of additional covariates may have improved likelihood without substantial overfitting. The gradient component (5.18e−05) remained within acceptable bounds, supporting convergence. These results suggest a trade-off between model complexity and fit, where models incorporating ecological covariates (s1.2 and s1.4) improved the likelihood function but required more parameters, while the simpler model (s1.1) retained strong convergence properties with fewer degrees of freedom.

```{r diagnostics, eval=TRUE, warning=FALSE, message=FALSE}
diagnostics <- read_csv("model_diagnosis.csv")
#write_csv(diagnostics, "model_diagnosis.csv")
flextable(diagnostics) %>%
  set_caption("diffenrent statistical componentes to evaluate perfomances and diagnostic of model scenarios") %>%
  autofit() %>%
  theme_booktabs() %>%
  fontsize(size = 10, part = "all") %>%
  set_table_properties(width = .85, layout = "autofit")
```

# DISCUSION

@@

@@

# CONCLUSION

@@

# ACKNOWLEDGMENTS

@@

# SUPPLEMENTARY MATERIAL

@@

@@

# REFERENCES

>>>>

# Abstract

@@

# Introduction

@@

# Methodology

@@

# Results

@@

The residuals are visualized by year and length bin, allowing an assessment of model fit over time and across the size structure of the population (Figure \@ref(fig:pearson)). In scenario s1.1 (Without Ecosystem Variables), substantial lack of fit is evident across multiple years and length classes, particularly in the late 1990s and early 2000s. Positive Pearson residuals indicate that the model tends to underestimate frequencies of certain length bins, especially among smaller and mid-sized individuals, suggesting poor representation of recruitment and growth dynamics in the absence of environmental and predator effects. s1.2 (With Predator) shows some improvement in model fit, with slightly more balanced residuals. However, there are still consistent deviations in the mid-size ranges across multiple years, indicating that predation alone does not fully explain observed variability in length composition. In s1.3 (With Environment), there is a noticeable reduction in residual magnitude across several years and size classes, implying that incorporating environmental covariates helps align the model more closely with observed size distributions. This is particularly apparent in the early 2000s, where the residuals are closer to zero across most bins. Finally, s1.4 (With Predator and Ecosystem) shows the most consistent reduction in Pearson residuals across time and size structure. The residual patterns also indicate potentially concerning model misfits, particularly among adult individuals in several survey fleets operating in the Bransfield Strait, as well as among the largest size classes in the predator fleet, which likely represents penguin consumption data. The residuals exhibit consistent over- or under-estimation in specific length bins over multiple years, suggesting that the current model structure may not fully capture key processes affecting the abundance or selectivity of adult individuals. In the case of surveys in Bransfield, this could reflect spatial mismatches between predicted and observed size distributions or biases in survey selectivity for larger size classes. This spatial heterogeneity aligns with previous findings identifying this area as a core juvenile krill habitat [@Mardones2025; @Veytia2021, Vetia et al., 2019, REF, REF]. Similarly, the residuals associated with the predator fleet suggest that the model may inadequately represent size-selective predation or the temporal dynamics of predator consumption. These patterns warrant further investigation into the assumptions underlying length selectivity and mortality, particularly for the adult component of the population, as well as potential ecosystem-driven variability not currently integrated in the model.

Overall, the distribution of residuals is more homogeneous and centered around zero, indicating that the combined inclusion of predator and environmental drivers leads to the best model fit among the four scenarios.

```{r pearson, eval=TRUE, fig.cap= "Pearson residuals of predicted versus observed length-frequency distributions of Antarctic krill across four modeling scenarios (s1.1 to s1.4), each incorporating increasing levels of ecosystem complexity. Residuals are shown by fleet, survey, and predator source, allowing visual assessment of model fit across time and sampling components (Red = positive, Black = negative"}
knitr::include_graphics('Figs/Pearson.png')
```

@@

The comparative evaluation of the four model scenarios (s1.1–s1.4) revealed key differences in model performance and complexity (Table \@ref(tab:diagnostics)).  All four scenarios achieved convergence, as indicated by a maximum gradient component of zero, ensuring that optimization reached a stable solution. Notably, the number of estimated parameters varied across models, with the full ecosystem model (s1.4) estimating the same number of parameters as the predator-only model (s1.2), while the environment-only model (s1.3) and the base model (s1.1) used fewer parameters. The Akaike Information Criterion (AIC) reveals stark contrasts in model performance. The environment-inclusive models (s1.3 and s1.1) have substantially lower AIC values (3,234.9 and 2,668.1, respectively) compared to the predator-inclusive models (s1.2 and s1.4), which exceed 50,000. These results suggest that environmental covariates contribute more effectively to explaining krill population dynamics than predator effects alone. The total likelihood (−logL) further supports this, showing much better fit in models s1.1 and s1.3, while predator-inclusive models (s1.2 and s1.4) show considerably poorer likelihood values. This pattern is reflected in the survey and length composition likelihood components, where again the environment-only model (s1.3) shows superior performance compared to predator scenarios. Root Mean Square Error (RMSE) for both index and length composition highlights better predictive accuracy in models without predators. Model s1.1 and s1.3 achieve lower RMSE values for both indices and length composition, indicating better alignment with observed data. In contrast, RMSE values are higher in predator-inclusive models (s1.2 and s1.4), suggesting poorer fit. Similarly, the Mean Absolute Scaled Error (MASE) remains lower in s1.1 and s1.3 (0.427), compared to s1.2 and s1.4 (0.517), again highlighting improved predictive performance in models that exclude predator effects. Retrospective biases (rho values) provide insight into model consistency over time. Retrospective bias in spawning stock biomass (Retro_Rho_ssb) and forecast biomass (Forecast_Rho_ssb) is substantially reduced in models without predators, particularly s1.1 (−0.233 and −0.333). Models including predators (s1.2 and s1.4) show larger negative rho values, indicating stronger retrospective bias and less stability in biomass estimation. Fishing mortality bias (Rho_f) and its forecast also present serious concerns in predator-inclusive scenarios. Model s1.4, for instance, shows a high retrospective bias in fishing mortality (Rho_f = 6.912), compared to 1.585 in the base model (s1.1). This indicates over-sensitivity in mortality estimates when predator effects are included without sufficient constraint or supporting data.

```{r diagnostics, eval=TRUE, warning=FALSE, message=FALSE}
diagnostics <- read_csv("model_diagnosis.csv")
#write_csv(diagnostics, "model_diagnosis.csv")
flextable(diagnostics) %>%
  colformat_num(digits = 3) |>  
  set_caption("Statistical componentes to evaluate perfomances and diagnostic of model scenarios") %>%
  autofit() %>%
  theme_booktabs() %>%
  fontsize(size = 10, part = "all") %>%
  set_table_properties(width = .85, layout = "autofit")
```

# Discusion

@@

Tabla summary

The analysis suggests that incorporating environmental variables (s1.3 and s1.4) improves model fit and predictive accuracy, particularly when compared to predator-only models. The model that includes only environmental covariates (s1.3) strikes the best balance between fit quality, complexity, and retrospective performance, suggesting that environmental variability is a key driver of krill population dynamics in the Western Antarctic Peninsula.

In contrast, the inclusion of predators alone (s1.2) leads to poorer model fit and higher retrospective bias, possibly due to data limitations or unaccounted complexity in predator-prey dynamics. While the full ecosystem model (s1.4) shows some improvements over the predator-only model, it still exhibits significant retrospective biases, highlighting the need for refined integration of ecosystem components and further data support, particularly regarding predator consumption rates and spatial foraging behavior.

These findings support growing consensus that ecosystem-informed stock assessments, particularly those that integrate environmental covariates, provide more robust and ecologically realistic estimates for Antarctic krill and should inform precautionary management frameworks under CCAMLR.

@@

# Conclusion

@@

# Acknowledgments

@@

# Supplementary Material

@@

# Data Availability

Data will be made available on request.

@@

# References

### 2025-04-15 index.Rmd
add table summary

Heatmap

create_heatmap <- function(df) {
  df1 <- df %>%
    dplyr::filter(Pearson < 5) %>%
    dplyr::select(c(1, 6, 19, 16)) %>%
    dplyr::mutate(Fleet = dplyr::case_when(
      Fleet == 1 ~ "FISHERYBS",
      Fleet == 2 ~ "FISHERYEI",
      Fleet == 3 ~ "FISHERYGS",
      Fleet == 4 ~ "FISHERYJOIN",
      Fleet == 5 ~ "FISHERYSSIW",
      Fleet == 6 ~ "SURVEYBS",
      Fleet == 7 ~ "SURVEYEI",
      Fleet == 8 ~ "SURVEYGS",
      Fleet == 9 ~ "SURVEYJOIN",
      Fleet == 10 ~ "SURVEYSSIW",
      Fleet == 11 ~ "PREDATOR",
      TRUE ~ NA_character_
    ))

  ggplot(df1, aes(x = Yr, y = Bin, fill = Pearson)) +
    geom_tile() +
    scale_fill_gradient2(low = "black", 
                         mid = "white", 
                         high = "red", 
                         midpoint = 0) +
    facet_wrap(Fleet~., ncol=6) + 
    labs(title = "", 
         x = "", 
         y = "Length (cm)", 
         fill = "Pearson") + 
    theme_few() + 
    theme(axis.text.x = element_text(angle = 90, 
                                     hjust = 1, 
                                     size = 7),
          legend.position = "bottom")
}

# Crear heatmaps para los diferentes dataframes
heatmap1 <- create_heatmap(base.model1.1$lendbase)
heatmap2 <- create_heatmap(base.model1.2$lendbase)
heatmap3 <- create_heatmap(base.model1.3$lendbase)
heatmap4 <- create_heatmap(base.model1.4$lendbase)

# Combina los plots en un solo gráfico con 8 columnas y 1 fila, compartiendo la leyenda
ggarrange(heatmap1, heatmap2, heatmap3, heatmap4, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom")
```

@@

```{r eval=FALSE}
# Assuming your data is in a data frame called 'lendbase'
# Filter and select relevant columns
data <- base.model1.4$lendbase %>%
  dplyr::filter(Pearson<5) %>% 
  dplyr::select(c(1, 6, 19, 16)) %>% 
  dplyr::mutate(Fleet = dplyr::case_when(
    Fleet == 1 ~ "FISHERYBS",
    Fleet == 2 ~ "FISHERYEI",
    Fleet == 3 ~ "FISHERYGS",
    Fleet == 4 ~ "FISHERYJOIN",
    Fleet == 5 ~ "FISHERYSSIW",
    Fleet == 6 ~ "SURVEYBS",
    Fleet == 7 ~ "SURVEYEI",
    Fleet == 8 ~ "SURVEYGS",
    Fleet == 9 ~ "SURVEYJOIN",
    Fleet == 10 ~ "SURVEYSSIW",
    Fleet == 11 ~ "PREDATOR",
    TRUE ~ NA_character_  # Para manejar cualquier valor que no coincida
  )) %>% 
  dplyr::select(Yr, Bin, Pearson)

# Create the hexagonal heatmap
ggplot(data, aes(x = Yr, y = Bin)) +
  geom_hex(bins=50) +  # Hexagonal bins
  scale_fill_gradient2(low = "blue", 
                       mid = "white", 
                       high = "red", 
                       midpoint = 0) +  # Color scale
  theme_minimal() +  # Minimal theme for cleaner look
  labs(title = "Hexagonal Heatmap of Pearson Residuals",
       x = "Year",
       y = "Bin",
       fill = "Pearson Residual")  # Labels for plot and axes

@@

```{r}
par(mfrow=c(2,2), mar=c(5,4,2,1))
SSplotJABBAres(base.model1.1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1.4,
               subplots = "len",
               add=T)
```

```{r}
par(mfrow=c(2,2), mar=c(5,4,2,1))
SSplotJABBAres(base.model1.1,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.2,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.3,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1.4,
               subplots = "cpue",
               add=T)
```

@@

```{r}
par(mfrow=c(2,4), mar=c(5,4,2,1))
hci = SSplotHCxval(retroSummary1.1, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(3,3), mar=c(5,4,2,1))
hci = SSplotHCxval(retroSummary1.2, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(2,4), mar=c(5,4,2,1))
hci = SSplotHCxval(retroSummary1.3, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(3,3), mar=c(5,4,2,1))
hci = SSplotHCxval(retroSummary1.4, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7) 
```

@@

### `SSplotProfile()`

@@

```{r}
# Construcción de tabla resumen
diagnostics <- data.frame(
  Model = c("s1.1", "s1.2", "s1.3", "s1.4"),
  Gradient = c(
    base.model1.1$maximum_gradient_component,
    base.model1.2$maximum_gradient_component,
    base.model1.3$maximum_gradient_component,
    base.model1.4$maximum_gradient_component
  ),
  Likelihood = c(
    base.model1.1$likelihoods_used[1,1],
    base.model1.2$likelihoods_used[1,1],
    base.model1.3$likelihoods_used[1,1],
    base.model1.4$likelihoods_used[1,1]
  ),
  Parameters = c(
    dim(base.model1.1$parameters)[1],
    dim(base.model1.2$parameters)[1],
    dim(base.model1.3$parameters)[1],
    dim(base.model1.4$parameters)[1]
  ),
  RMSE = c(
    mean(as.numeric(base.model1.1$index_variance_tuning_check$RMSE)),
    mean(as.numeric(base.model1.2$index_variance_tuning_check$RMSE[1:10])),
    mean(as.numeric(base.model1.3$index_variance_tuning_check$RMSE[1:10])),
    mean(as.numeric(base.model1.4$index_variance_tuning_check$RMSE[1:10]))
  )
)
#write_csv(diagnostics, "model_diagnosis.csv")
flextable(diagnostics) %>%
  set_caption("Diagnostic summary of model scenarios") %>%
  autofit() %>%
  theme_booktabs() %>%
  fontsize(size = 10, part = "all") %>%
  set_table_properties(width = .85, layout = "autofit")

>>>>

Pearson residual

```{r}
create_heatmap_df <- function(df, model_name) {
  df %>%
    dplyr::filter(Pearson < 5) %>%
    dplyr::select(c(1, 6, 19, 16)) %>%
    dplyr::mutate(Fleet = dplyr::case_when(
      Fleet == 1 ~ "FISHERYBS",
      Fleet == 2 ~ "FISHERYEI",
      Fleet == 3 ~ "FISHERYGS",
      Fleet == 4 ~ "FISHERYJOIN",
      Fleet == 5 ~ "FISHERYSSIW",
      Fleet == 6 ~ "SURVEYBS",
      Fleet == 7 ~ "SURVEYEI",
      Fleet == 8 ~ "SURVEYGS",
      Fleet == 9 ~ "SURVEYJOIN",
      Fleet == 10 ~ "SURVEYSSIW",
      Fleet == 11 ~ "PREDATOR",
      TRUE ~ NA_character_
    )) %>%
    dplyr::mutate(Model = model_name)
}

# Unir los datasets en uno solo
df_all <- bind_rows(
  create_heatmap_df(base.model1.1$lendbase, "Model 1.1"),
  create_heatmap_df(base.model1.2$lendbase, "Model 1.2"),
  create_heatmap_df(base.model1.3$lendbase, "Model 1.3"),
  create_heatmap_df(base.model1.4$lendbase, "Model 1.4")
)

# Plot combinado: facet_grid por Modelo y Fleet
heatmapres <- ggplot(df_all, aes(x = Yr, y = Bin, fill = Pearson)) +
  geom_tile() +
  scale_fill_gradient2(low = "red", 
                       mid = "white", 
                       high = "blue",
                       midpoint = 0) +
  facet_grid(Fleet ~ Model) +
  theme_few() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, size = 5),         
    axis.text.y = element_text(size = 5),                               
    strip.text = element_text(size = 8),                                 
    legend.position = "none"
  ) +
  labs(x = "", y = "Length (cm)", fill = "Pearson")

heatmapres
```

@@

@@

```{r}
par(mfrow=c(2,2), mar=c(5,4,2,1))
rmse1l <- SSplotJABBAres(base.model1.1,
               subplots = "len",
               add=T)
rmse2l <- SSplotJABBAres(base.model1.2,
               subplots = "len",
               add=T)
rmse3l <- SSplotJABBAres(base.model1.3,
               subplots = "len",
               add=T)
rmse4l <- SSplotJABBAres(base.model1.4,
               subplots = "len",
               add=T)
```

```{r}
par(mfrow=c(2,2), mar=c(5,4,2,1))
rmse1c <- SSplotJABBAres(base.model1.1,
               subplots = "cpue",
               add=T)
rmse2c <- SSplotJABBAres(base.model1.2,
               subplots = "cpue",
               add=T)
rmse3c <- SSplotJABBAres(base.model1.3,
               subplots = "cpue",
               add=T)
rmse4c <- SSplotJABBAres(base.model1.4,
               subplots = "cpue",
               add=T)
```

@@

```{r}
par(mfrow=c(2,4), mar=c(5,4,2,1))
hci1 = SSplotHCxval(retroSummary1.1, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(3,3), mar=c(5,4,2,1))
hci2 = SSplotHCxval(retroSummary1.2, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(2,4), mar=c(5,4,2,1))
hci3 = SSplotHCxval(retroSummary1.3, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

```{r}
par(mfrow=c(3,3), mar=c(5,4,2,1))
hci4 = SSplotHCxval(retroSummary1.4, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7) 
```

@@

@@

```{r}
# Modelo s1.1
diag1.1 <- data.frame(
  Scenario = "s1.1",
  Convergency = base.model1.1$maximum_gradient_component,
  AIC = as.numeric(2 * dim(base.model1.1$estimated_non_dev_parameters)[1] + 2 * base.model1.1$likelihoods_used[1, 1]),
  Total_like = base.model1.1$likelihoods_used$values[rownames(base.model1.1$likelihoods_used) == "TOTAL"],
  N_Params = as.numeric(2 * dim(base.model1.1$estimated_non_dev_parameters)[1]),
  Survey_like = base.model1.1$likelihoods_used$values[rownames(base.model1.1$likelihoods_used) == "Survey"],
  Length_comp_like = base.model1.1$likelihoods_used$values[rownames(base.model1.1$likelihoods_used) == "Length_comp"],
  RMSE_index = rmse1c$RMSE.perc[rmse1c$indices == "Combined"],
  RMSE_length = rmse1l$RMSE.perc[rmse1l$indices == "Combined"],
  MASE = mean(hci1$MAE.base, na.rm = TRUE),
  Retro_Rho_ssb = tablebias01[5, 3],
  Forecast_Rho_ssb = tablebias01[5, 4],
  Forecast_Rho_f = tablebias01a[5, 3],
  Rho_f = tablebias01a[5, 4]
)

# Modelo s1.2
diag1.2 <- data.frame(
  Scenario = "s1.2",
  Convergency = base.model1.2$maximum_gradient_component,
  AIC = as.numeric(2 * dim(base.model1.2$estimated_non_dev_parameters)[1] + 2 * base.model1.2$likelihoods_used[1, 1]),
  Total_like = base.model1.2$likelihoods_used$values[rownames(base.model1.2$likelihoods_used) == "TOTAL"],
  N_Params = as.numeric(2 * dim(base.model1.2$estimated_non_dev_parameters)[1]),
  Survey_like = base.model1.2$likelihoods_used$values[rownames(base.model1.2$likelihoods_used) == "Survey"],
  Length_comp_like = base.model1.2$likelihoods_used$values[rownames(base.model1.2$likelihoods_used) == "Length_comp"],
  RMSE_index = rmse2c$RMSE.perc[rmse2c$indices == "Combined"],
  RMSE_length = rmse2l$RMSE.perc[rmse2l$indices == "Combined"],
  MASE = mean(hci2$MAE.base, na.rm = TRUE),
  Retro_Rho_ssb = tablebias2[5, 3],
  Forecast_Rho_ssb = tablebias2[5, 4],
  Forecast_Rho_f = tablebias2a[5, 3],
  Rho_f = tablebias2a[5, 4]
)

# Modelo s1.3
diag1.3 <- data.frame(
  Scenario = "s1.3",
  Convergency = base.model1.3$maximum_gradient_component,
  AIC = as.numeric(2 * dim(base.model1.3$estimated_non_dev_parameters)[1] + 2 * base.model1.3$likelihoods_used[1, 1]),
  Total_like = base.model1.3$likelihoods_used$values[rownames(base.model1.3$likelihoods_used) == "TOTAL"],
  N_Params = as.numeric(2 * dim(base.model1.3$estimated_non_dev_parameters)[1]),
  Survey_like = base.model1.3$likelihoods_used$values[rownames(base.model1.3$likelihoods_used) == "Survey"],
  Length_comp_like = base.model1.3$likelihoods_used$values[rownames(base.model1.3$likelihoods_used) == "Length_comp"],
  RMSE_index = rmse3c$RMSE.perc[rmse3c$indices == "Combined"],
  RMSE_length = rmse3l$RMSE.perc[rmse3l$indices == "Combined"],
  MASE = mean(hci3$MAE.base, na.rm = TRUE),
  Retro_Rho_ssb = tablebias3[5, 3],
  Forecast_Rho_ssb = tablebias3[5, 4],
  Forecast_Rho_f = tablebias3a[5, 3],
  Rho_f = tablebias3a[5, 4]
)

# Modelo s1.4
diag1.4 <- data.frame(
  Scenario = "s1.4",
  Convergency = base.model1.4$maximum_gradient_component,
  AIC = as.numeric(2 * dim(base.model1.4$estimated_non_dev_parameters)[1] + 
                     2 * base.model1.4$likelihoods_used[1, 1]),
  Total_like = base.model1.4$likelihoods_used$values[rownames(base.model1.4$likelihoods_used) == "TOTAL"],
  N_Params = as.numeric(2 * dim(base.model1.4$estimated_non_dev_parameters)[1]),
  Survey_like = base.model1.4$likelihoods_used$values[rownames(base.model1.4$likelihoods_used) == "Survey"],
  Length_comp_like = base.model1.4$likelihoods_used$values[rownames(base.model1.4$likelihoods_used) == "Length_comp"],
  RMSE_index = rmse4c$RMSE.perc[rmse4c$indices == "Combined"],
  RMSE_length = rmse4l$RMSE.perc[rmse4l$indices == "Combined"],
  MASE = mean(hci4$MAE.base, na.rm = TRUE),
  Retro_Rho_ssb = tablebias4[5, 3],
  Forecast_Rho_ssb = tablebias4[5, 4],
  Forecast_Rho_f = tablebias4a[5, 3],
  Rho_f = tablebias4a[5, 4]
)

diag_all <- rbind(diag1.1,
                  diag1.2, 
                  diag1.3, 
                  diag1.4)

diag_tidy <- diag_all |>
  pivot_longer(cols = -Scenario, names_to = "Description", values_to = "Value") |>
  pivot_wider(names_from = Scenario, values_from = Value)

diag_tidy[, 2:5] <- lapply(diag_tidy[, 2:5], function(x) as.numeric(format(round(x, 3), nsmall = 3)))

#write_csv(diag_tidy, "model_diagnosis.csv")
flextable(diag_tidy) |>
  colformat_num(digits = 3) |>  
  autofit() |>
  theme_booktabs() |>
  align(align = "center", part = "all") |>
  bold(part = "header")
```
